---
title: <center>COVID-19 Report</center>
author: <center>SAI Law & Economics</center>
date: <center>`r Sys.setlocale('LC_TIME','English'); format(Sys.time(),'%B %d, %Y')`</center>
output:
   html_document:
      toc: true
      toc_depth: 2
      toc_float:
         collapse: false
         smooth_scroll: true
---

```{r setup, include=FALSE}

##### R Markdown global options #####

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, include = TRUE, fig.align = 'center', out.width = '100%')

##### libraries #####

library(tidyverse)
library(plotly)
library(extrafont)
library(mgcv)
loadfonts(device = 'win') # The first time you install this package, you have to execute font_import()

##### data import #####

mobility_raw_data <- read_csv('inputs/global_mobility_report.csv')

covid_data <- read_csv('inputs/owid-covid-data.csv')

##### Colors #####

colors_pal <- c('#004170','#098d9c','#cc003a','#b2d600','#ffcc00','#00c954','#00bf9f','#00a9bf','#6f00bf','#b02c88')

colors_continent <- sample(colors_pal,6,replace = FALSE)

##### Dummy function #####

do_nothing <- function(df) { return(df) }

```

<br>

Sources:

* Our World in Data. Data collected, aggregated, and documented by Diana Beltekian, Daniel Gavrilov, Charlie Giattino, Joe Hasell, Bobbie Macdonald, Edouard Mathieu, Esteban Ortiz-Ospina, Hannah Ritchie, Max Roser. https://github.com/owid/covid-19-data/tree/master/public/data. Accessed: `r Sys.setlocale('LC_TIME','English'); format(Sys.time(), '%B %d, %Y')`.

* Google LLC "Google COVID-19 Community Mobility Reports". https://www.google.com/covid19/mobility/ Accessed: `r Sys.setlocale('LC_TIME','English'); format(Sys.time(), '%B %d, %Y')`.

# Intro

[Text]

# COVID-19 

```{r data_frame}

covid1 <- covid_data %>%
   arrange(location,date) %>% 
   group_by(location) %>%
   mutate(max_cases = max(total_cases,na.rm = TRUE),
          max_deaths = max(total_deaths,na.rm = TRUE),
          max_cases_per_million = max(total_cases_per_million,na.rm = TRUE),
          max_deaths_per_million = max(total_deaths_per_million,na.rm = TRUE)) %>%
   filter(location != 'World') %>% 
   do_nothing()

```

[Text]

## Total cases

[Text]

```{r total_cases_by_country_plot, fig.height=8}

covid1 %>% 
   filter( (max_cases_per_million > 1000 &
               max_cases > 40000 &
               population > 5000000 &
               total_cases >= 100) |
              location == 'China' ) %>%
   ggplot(aes(x = date, y = total_cases/1000, color = continent)) +
   geom_line(size = 2) +
   facet_wrap(~fct_reorder(location,max_cases, .desc = TRUE), scales = 'free_y') +
   scale_y_continuous(labels = scales::comma_format(accuracy = 1)) +
   scale_color_manual(values = colors_continent) +
   theme_minimal() +
   theme(panel.grid = element_blank(),
         panel.background = element_rect(fill = '#fafafa', color = 'white'),
         strip.background = element_rect(fill = '#fafafa', color = 'white'),
         strip.text = element_text(family = 'Century Gothic', color = '#002126'),
         legend.position = 'bottom',
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text = element_text(family = 'Century Gothic', color = '#002126'),
         text = element_text(family = 'Century Gothic', color = '#002126'),
         plot.title = element_text(hjust = 0.5, face = 'bold'),
         plot.caption = element_text(hjust = 0),
         NULL) +
   ylab('Total cases (\'000)\n') +
   labs(title = 'Total cases\' evolution since the 100th case, by country\n',
        caption = '* Only countries with more than 40,000 cases, more than 1,000 cases per million habitants,\nand with a total population greater than 5 million people are shown (except for China).\n\nData source: Our World in Data.')

```

## Subsection

<br><br>

<center>**Statistics by Country**</center>

<br>

```{r covid_table}

covid1 %>% 
   filter(date == last(date)) %>% 
   select(date, location, total_cases, total_cases_per_million, total_deaths, total_deaths_per_million) %>% 
   arrange(-total_cases) %>% 
   rename_all(funs(c('Date', 'Country', 'Total Cases', 'Total Cases per Million', 'Total Deaths', 'Total Deaths per Million'))) %>% 
   DT::datatable(., rownames = FALSE,
                 filter = 'top',
                 width = 825,
                 options = list(pageLength = 20,
                                scrollX = TRUE,
                                searching = TRUE,
                                lengthMenu = c(10,20,30,40,50),
                                columnDefs = list(list(className = 'dt-center', targets = 0:5)))) %>% 
   DT::formatRound(table = ., columns = c('Total Deaths per Million'), digits = 2) %>% 
   DT::formatCurrency(table = ., columns = c('Total Cases','Total Cases per Million', 'Total Deaths'), currency = '', digits = 0) %>% 
   DT::formatStyle(0:5, color = '#002126')
   
```

```{r}

p <- covid1 %>% 
   group_by(continent,.add = TRUE) %>% 
   summarise(total_deaths = max(total_deaths,na.rm = TRUE), .groups = 'keep') %>% 
   mutate('Total deaths' = round(total_deaths/1000,digits = 1)) %>% 
   filter(total_deaths > 1000 & !is.na(continent)) %>% 
   ggplot(aes(x = fct_reorder(location,total_deaths,.desc = TRUE), y = `Total deaths`, fill = continent)) +
   geom_col() +
   scale_y_continuous(labels = scales::comma_format(accuracy = 1)) +
   scale_fill_manual(values = colors_continent) +
   theme_minimal() +
   theme(panel.grid = element_blank(),
         legend.title = element_blank(),
         axis.title.x = element_blank(),
         axis.text.x = element_text(angle = 90,vjust = 0),
         text = element_text(family = 'Century Gothic', color = '#002126'),
         plot.title = element_text(hjust = 0.5, face = 'bold'),
         plot.subtitle = element_text(hjust = 0.5, face = 'bold'),
         plot.caption = element_text(hjust = 0),
         NULL) +
   ylab('Total deaths (\'000)\n') +
   labs(title = 'Total deaths by country\n',
        caption = '* Only countries with more than 1,000 deaths are shown.\n\nData source: Our World in Data.')

ggplotly(p,tooltip = c('text','y'))

```

# Global Mobility

```{r}

plots_lst <- list()

vars <- set_names(names(select(mobility_raw_data,                            retail_and_recreation_percent_change_from_baseline:residential_percent_change_from_baseline)),
                  c('Retail and Recreation',
                    'Grocery and Pharmacy',
                    'Parks',
                    'Transit Stations',
                    'Work Places',
                    'Residential Activities'))

for (i in names(vars)) {

   plots_lst[[i]] <- covid1 %>%
      group_by(continent,.add = TRUE) %>%
      select(continent:new_deaths_per_million, max_cases:max_cases_per_million, population) %>%
      filter(total_cases >= 100 & population > 10000000) %>%
      filter(date == min(date) & max_cases_per_million < 10000 & max_cases_per_million > 1000) %>%
      left_join(select(filter(mobility_raw_data,is.na(sub_region_1)),
                       country_region,date,8:13),
                by = c('location' = 'country_region', 'date' = 'date')) %>%
      filter(across(ends_with('baseline'),~!is.na(.))) %>%
      ggplot(aes_string(x = vars[[i]], y = 'max_cases_per_million', color = 'continent')) +
      geom_text(aes(label = location, color = continent, size = max_deaths)) +
      scale_color_manual(values = colors_continent, name = '') +
      scale_y_continuous(labels = scales::comma) +
      scale_size(range = c(1,10), name = 'Current total deaths', labels = scales::comma) +
      theme_minimal() +
      theme(panel.grid = element_blank(),
            text = element_text(family = 'Century Gothic', color = '#002126'),
            plot.title = element_text(hjust = 0.5, face = 'bold'),
            plot.subtitle = element_text(hjust = 0.5, face = 'bold'),
            plot.caption = element_text(hjust = 0),
            NULL) +
      ylab('Current total cases per million habitants\n') + xlab(paste0('\n Average decrease in ',i,' mobility\n\n')) +
      labs(title = paste0('Relation between changes in ', i, ' after\nthe 100th detected case,\nand total cases per million habitants and total deaths\n'),
           caption = '*Only countries with total cases per million habitants between 1000 and 10,000, and wit a population\ngreater than 1 million people are shown.\n\nData source: Our World in Data & Google Mobility Reports.')

}

# plot <- function(variable){
#    
#    # Código para hacer gráfica
#    
# }
# 
# plots_lst <- map(vars, ~plot(.))

```


## Subsection 1 {.tabset .tabset-fade}

[Text]

```{r results='asis'}

for (plot in names(plots_lst)) {

   cat('\n')

   cat('### ', plot, '\n')

   print(plots_lst[[plot]])

   cat('\n')

}

```
